HUME: Human UCCA-based Machine-Translation Evaluation

### 2016-03-08 paper/main.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}\label{sec:experiments}

@@

\subsection{Efficient of Annotation}\label{sec:efficiency}

\subsection{Agreement across Languages }\label{sec:efficiency}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}\label{sec:experiments}
\subsection{Data Sets and Translation Systems}
\begin{itemize}
  \item Briefly describe translation systems.
  \item Source texts (no need to describe references)
\end{itemize}

\subsection{Annotation Process}
\begin{itemize}
  \item Numbers of annotators, IDs
  \item Length of annotation, timings
  \item Sentences annotated
\end{itemize}

@@

\subsection{Efficiency of Annotation}\label{sec:efficiency}

\subsection{Inter-Annotator Agreement}
\begin{itemize}
  \item Multiple annotation stats
  \item Kappas -- ROG, AB
  \item Kappa versus length
  \item Kappa versus bleu?
\end{itemize}

@@

In order to assess the consistency of the annotation, we measure the Inter-Annotator
Agreement (IAA) using Cohen's Kappa on the multiply-annotated portions of the data.
For German, Polish and Romanian we used two annotators, so we report IAA on the overlap
between these annotators. For Czech we used one main annotator, plus several other extra
annotators to provide IAA.

To calculate Kappa, we consider the annotation task as a classification task on 
nodes. We only consider nodes where there are at least two annotations from different
annotators and we treat nodes with more than two annotations as a set of paired
annotations\bh{This may not be correct, so should/could we do Kappa across the 
variable multiple annotations on Czech}. We consider Kappa separately on the lexical
nodes (annotated as red, orange or green) and the structural nodes (annotated
as acceptable or bad) since there should not be any confusion between these two types of
nodes. The small number of nodes which one annotator had labelled as structural and 
the other as lexical were ignored for the purposes of IAA, since such cases of annotator 
error could be caught by improved tool support.  The Kappas are shown in \tabref{tab:iaa}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{l|cccc}
 & cs & de & pl & ro \\
\hline
Sentences & & & & \\
\hline
Lexical nodes & & & & \\
Kappa & & & & \\
\hline
Structural nodes & & & & \\
Kappa & & & & \\
\end{tabular}
\caption{Inter-annotator agreement for the multiply-annotated portions of the data, as
measured by Cohen's Kappa. }
\label{tab:iaa}
\end{center}
\end{table}

To assess whether, as we hoped, HUME would make it easier to reliably annotate long sentences,
we binned the sentences according to length and measured Kappa on each of the bins.
